IML Term project paper

### 2022-12-11 paper.rmd
Update paper.rmd
Small changes

@@

In order to reduce knitting time for the file, we will in this preliminary report instead of expressing the full R code to calculate the values, simply report the results we received and instead return the full R code only with the final report. The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|cc|}
\hline
Model type & loo-cv accuracy & loo-cv perplexity\\
\hline
Dummy model & 0 & 2.01\\
Logistic regression & 0.89 & 1.30\\
Naive Bayes & 0.81 & 152.85\\
LDA & 0.89 & 1.33\\
QDA & 0.85 & 6.34\\
SVM & 0.88 & 1.34\\
Lasso & 0.89 & 1.29\\
Random Forest & 0.89 & 1.35\\

\end{tabular}
\end{table}

@@

We made the decision based on preliminary results, and though decision trees would represent an equally viable solution, we calculated those results only later on, and by that point had already calculated the results for the logistic regression model. However, for the final report we might consider transitioning to the decision tree model.

>>>>

### Classification trees

To be added later

@@

In order to reduce knitting time for the file, we will in this preliminary report instead of expressing the full R code to calculate the values, simply report the results we received and instead return the full R code only with the final report. The results for the two-class models in terms of loo-cross-validated accuracy and perplexity are:
\begin{table}
\begin{tabular}{|r|cc|}
\hline
Model type & loo-cv accuracy & loo-cv perplexity\\
\hline
Dummy model & 0 & 2.01\\
Logistic regression & 0.89 & 1.30\\
Naive Bayes & 0.81 & 152.85\\
LDA & 0.89 & 1.33\\
QDA & 0.85 & 6.34\\
SVM & 0.88 & 1.34\\
Lasso & 0.89 & 1.29\\
Classification trees & 0.89 & 1.35\\
\hline
\end{tabular}
\end{table}

@@

We made the decision of model based on preliminary results, and though classification trees would represent an equally viable solution, we calculated those results only later on, and by that point had already calculated the results for the logistic regression model. However, for the final report we might consider transitioning to the classification tree model.
